Some examples in extended logic counting classes

### 2017-01-08 LICS/extentions.tex
sc

There exist counting complexity classes that do not fit in our framework because either the output of a function in not a natural numbers (e.g. a negative number) or the class is not defined purely in terms of arithmetical operations (e.g. min and max).
To remedy this problem, we show here how to easily extend $\qso$ in order to capture these classes that go beyond sum and product over natural numbers.

>>>>

%!TEX root = main.tex

There exist complexity classes that do not fit in our framework because either the output of a function in not a natural number (e.g. a negative number) or the class is not defined purely in terms of arithmetical operations (e.g. min and max are used).
To remedy this problem, we show here how $\qso$ can be easily extended  to capture such classes that go beyond sum and product over natural numbers.
